method

### 2022-02-01 06_Paper/ER-ED/method.Rmd
Update method.Rmd

Young, healthy participants (aged 18 to 30 years) will be recruited using the software *ORSEE* [@Greiner2015].
Participants will be invited to fill out an online survey containing different questionnaires to assess broad and narrow personality traits and measures of well-being.
The study consisted of two sessions, one week apart. 
Both sessions took place in a shielded cabin with constant lighting. 
Before each session, participants received information about the respective experimental procedure and signed informed consent. 
At the beginning of the first session participants filled out a demographic questionnaire. 
Afterwards the completed an n-Back task with the levels one to four.
Then, they completed an ED procedure on screen, followed by a random repetition of one n-back level.
The second session, containing the ER paradigm, took place exactly one week after session one.
Participants gave signed informed consent for the second session.
Afterwards the ER paradigm was conducted.
Participants first received written instructions on the ER paradigm and ER strategies that they should apply.
A training session was performed to ensure that all participants were able to implement the ER strategies.
Next, electrodes to measure EMG were attached and the ER paradigm was conducted.

@@

*Part one: ER task.* <br>
Part one could be described as standard ER task that followed a block design (see Figure X), similar to paradigms previously used by our group [@Scheffel2021]. 
Participants were told to actively view neutral and negative pictures (see [2.4](##stimuli)) or to regulate all upcoming emotions by means of distraction, distancing and expressive suppression, respectively. 
Every participant first had the condition "active viewing-neutral" that served as a baseline condition.
During this block, 20 neutral pictures were presented.
Participants were asked to "actively view all pictures and permit all emotions that may arise."
In the second block, participants actively viewed negative pictures.
During the third, fourth, and fifth block, participants saw negative pictures and were asked to regulate their emotions using distraction, distancing, and suppression.
In order to achieve distraction, participants were asked to think of a geometric object or an everyday activity, like brushing their teeth.
During distancing, participants were asked to "take the position of a non-involved observer, thinking about the picture in a neutral way."
Participants were told not to re-interpret the situation or attaching a different meaning to the situation.
During suppression, participants were told to "suppress their emotional facial expression."
They should imagine being observed by a third person that should not be able to tell just by looking at the facial expression whether the person is looking at an emotional picture.
Participants were instructed not to suppress their thoughts or change their facial expression to the opposite [@Scheffel2021].
All participants received written instruction and completed a training session.
After the training session, participants were asked about their applied ER strategies to avoid misapplication.
The order of the three regulation blocks (distraction, distancing, and suppression) was randomized between participants.

@@

Participants received 30.00€ or course credit as compensation for participation.
Study data were collected and managed using REDCap electronic data capture tools hosted at Technische Universität Dresden [@Harris2009; @Harris2019].

@@

Participants will be healthy adults in the age of 18 to 30, recruited using the software *ORSEE* [@Greiner2015] at the Technische Universität Dresden. 
Participants will be excluded from participation if they do not fluently speak German, have current or a history of psychological disorders or neurological trauma, or report to take medication.
We will use all available data in subsequent analyses.
However, if participants withdraw from study participation, technical failures occur, or experimenter considers the participant for not suitable for study participation (e.g., because the participant does not follow instructions or shows great fatigue), respective data will also be excluded from further analyses.

## 2.4 Stimuli

## 2.5 Electromyography

## 2.6 Psychometric measures

Two days after the T2 ER session, participants receive an email containing the link to the online survey. 
This survey contained a number of questionnaires: General psychological well-being was assessed using the WHO-5 scale [@Bech2004; German version: @Braehler2007].
To capture the construct of resilience, the 10-item-form of the Connor-Davidson resilience Scale (CD-RISC)[@Connor2003,@Campbell-Sills2007; German version: @Sarubin2015] was used. 
Dispositional use of ER was assessed using the Emotion Regulation Questionnaire (ERQ) [@GrossJohn2003;German version: @Abler2009].
For the assessment of ER ability we used the Flexible Emotion Regulation Scale (FlexER) [@Doerfel2019].
Implicit theories of willpower in emotion control were assessed using the implicit theories questionnaire from Bernecker and Job [-@Bernecker2017] was used.
To assess need for cognition, the short form of the Need for Cognition Scale [@Cacioppo1982; German version: @Bless1994] was used.
To assess self-control, sum scores of the following questionnaires were used [@Paschke2016]: the Self-Regulation Scale (SRS) [@Schwarzer1999], the Brief Self-Control Scale (BSCS) @Tangney2004; German version: @Sproesser2011], and the Barratt Impulsiveness Scale (BIS-11) [@Patton1995; German version: @Hartmann2011].
Attentional control was assessed using the Attentional Control Scale (ACS) [@Derryberry2002].

>>>>

Young, healthy participants (aged 18 to 30 years) will be recruited using the software *ORSEE* [@Greiner2015] at the Technische Universität Dresden.
Participants will be invited to fill out an online survey containing different questionnaires to assess broad and narrow personality traits and measures of well-being.
The study consisted of two sessions, one week apart. 
Both sessions took place in a shielded cabin with constant lighting. 
Before each session, participants received information about the respective experimental procedure and signed informed consent. 
At the beginning of the first session participants filled out a demographic questionnaire. 
Afterwards the completed an n-Back task with the levels one to four.
Then, they completed an ED procedure on screen, followed by a random repetition of one n-back level.
The second session, containing the ER paradigm, took place exactly one week after session one.
Participants gave signed informed consent for the second session.
Afterwards the ER paradigm was conducted.
Participants first received written instructions on the ER paradigm and ER strategies that they should apply.
A training session was performed to ensure that all participants were able to implement the ER strategies.
Next, electrodes to measure EMG were attached and the ER paradigm was conducted. 
Participants received 30.00€ or course credit as compensation for participation.
Study data were collected and managed using REDCap electronic data capture tools hosted at Technische Universität Dresden [@Harris2009; @Harris2019].

### 2.3.1 Psychometric measures

The online survey contained a number of questionnaires: General psychological well-being was assessed using the WHO-5 scale [@Bech2004; German version: @Braehler2007].
To capture the construct of resilience, the 10-item-form of the Connor-Davidson resilience Scale (CD-RISC)[@Connor2003,@Campbell-Sills2007; German version: @Sarubin2015] was used. 
Dispositional use of ER was assessed using the Emotion Regulation Questionnaire (ERQ) [@GrossJohn2003;German version: @Abler2009].
For the assessment of ER ability we used the Flexible Emotion Regulation Scale (FlexER) [@Doerfel2019].
Implicit theories of willpower in emotion control were assessed using the implicit theories questionnaire from Bernecker and Job [-@Bernecker2017] was used.
To assess need for cognition, the short form of the Need for Cognition Scale [@Cacioppo1982; German version: @Bless1994] was used.
To assess self-control, sum scores of the following questionnaires were used [@Paschke2016]: the Self-Regulation Scale (SRS) [@Schwarzer1999], the Brief Self-Control Scale (BSCS) @Tangney2004; German version: @Sproesser2011], and the Barratt Impulsiveness Scale (BIS-11) [@Patton1995; German version: @Hartmann2011].
Attentional control was assessed using the Attentional Control Scale (ACS) [@Derryberry2002].

### 2.3.2 Emotion regulation paradigm

@@

*Part one: ER task.* <br>
Part one could be described as standard ER task that followed a block design (see Figure X), similar to paradigms previously used by our group [@Scheffel2021]. 
Participants were told to actively view neutral and negative pictures (see [2.3.3](##stimuli)) or to regulate all upcoming emotions by means of distraction, distancing and expressive suppression, respectively. 
Every participant first had the condition "active viewing-neutral" that served as a baseline condition.
During this block, 20 neutral pictures were presented.
Participants were asked to "actively view all pictures and permit all emotions that may arise."
In the second block, participants actively viewed negative pictures.
During the third, fourth, and fifth block, participants saw negative pictures and were asked to regulate their emotions using distraction, distancing, and suppression.
In order to achieve distraction, participants were asked to think of a geometric object or an everyday activity, like brushing their teeth.
During distancing, participants were asked to "take the position of a non-involved observer, thinking about the picture in a neutral way."
Participants were told not to re-interpret the situation or attaching a different meaning to the situation.
During suppression, participants were told to "suppress their emotional facial expression."
They should imagine being observed by a third person that should not be able to tell just by looking at the facial expression whether the person is looking at an emotional picture.
Participants were instructed not to suppress their thoughts or change their facial expression to the opposite [@Scheffel2021].
All participants received written instruction and completed a training session.
After the training session, participants were asked about their applied ER strategies to avoid misapplication.
The order of the three regulation blocks (distraction, distancing, and suppression) was randomized between participants.

@@

### 2.3.3 Stimuli

### 2.3.4 Electromyography

@@

Participants will be healthy adults in the age of 18 to 30, recruited using the software *ORSEE* [@Greiner2015] at the Technische Universität Dresden. 
Participants will be excluded from participation if they do not fluently speak German, have current or a history of psychological disorders or neurological trauma, or report to take medication.
Sample size calculation with _G*Power_ [@Faul2007; @Faul2009]
However, if participants withdraw from study participation, technical failures occur, or experimenter considers the participant for not suitable for study participation (e.g., because the participant does not follow instructions or shows great fatigue), respective data will also be excluded from further analyses.
